mlr_assg4

### 2022-09-21 hw4-1/abhinav/mlr.Rmd
Final Code push-final

```
# Observations: 
Since , the above graph gives us a value of $\lambda \approx 0$ , therefore taking a log transformation of the dependent variable y makes more sense.

>>>>

```
# Observations: 
Since , the above graph gives us the best value of $\lambda$ to be around 0 only , therefore taking a log transformation of the dependent variable y makes more sense.
